Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2016-12-06 draft.tex
.

Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behaviour under sparse connectivity with a relatively high per-synapse connection strength, see e.g. \cite{Vreeswijk1996} or \cite{Brunel2000}. This kind of asynchronous regular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity. This feature was shown to be achieved after slowing down the rate of homeostatic adaption. On the level of single cells, interspike intervals should be random, approximately following the statistics of a poisson process.

>>>>

Balanced networks of inhibitory and excitatory populations of spiking LIF-neurons are known to show highly random, uncorrelated spiking behaviour under sparse connectivity with a relatively high per-synapse connection strength, see e.g. \cite{Vreeswijk1996} or \cite{Brunel2000}. This kind of asynchronous regular state is characterized by a population firing rate showing no regularities over time, though maintaining an overall stable level of activity. This feature was shown in the previous section after slowing down the rate of homeostatic adaption. On the level of single cells, interspike intervals should be random, approximately following the statistics of a poisson process.   
\begin{figure}
\includegraphics[width=\textwidth]{../../plots/Spike_Stats/isi_cv_compare.png}
\caption{A: Distribution of interspike intervals of excitatory neurons for diffusive and non-diffusive homeostasis, measured over $\mathrm{1000\,s}$. For diffusive homeostasis, only neurons with a mean firing rate in a certain range (see legend) were included into statistics to prevent overlapping of different firing rates. Black lines are fits of exponential functions. B: Distribution of coefficients of variation. Each sample represents the CV of one excitatory neuron.}
\label{ISI_CV_compare}
\end{figure}
Figure \ref{ISI_CV_compare} shows the distribution of interspike intervals (ISIs) and the distribution of coefficient of variation ($\mathrm{CV\equiv\sigma/\mu}$), both taken over the set of excitatory neurons. However, in order to provide comparability between the ISI distributions in the diffusive/non-diffusive case, we restricted the statistics of the latter one to neurons whose mean firing rate fall into a window with a width of 1 Hz. Apparently, an approximately exponential distribution of ISIs is preserved for diffusive homeostasis, which is characteristic for poisson processes \cite[p. 27]{Theor_Neur_Dayan}. For perfect poissonian spiking, the CV should give a value of 1. CVs that are smaller, as seen in Figure \ref{ISI_CV_compare}, indicate a tendency towards greater regularity.
